---
title: "Homework 3"
author: "Jessi Rumkin"
date: "May 22, 2025"
format:
  html:
    toc: true # use this to display a table of contents
execute:
  message: false # use this to make sure messages don't show up
  warning: false # use this to make sure warnings don't show up
---


Link to GitHub repository: 

# Set Up

```{r}
#read in packages
library(tidyverse)
library(here)
library(gt)
library(janitor)
library(readxl)

#read in data for personal data project
mydata <- read.csv("data/mydata.csv")

```


# Problem 1: Personal Data

## a. Data summarizing 

I will be comparing the mean productivity score between two main groups, when I was alone and when I was accompanied for the study sessions in order to determine if working with other people increases my productivity, which is calculated from time spent working and how focused I was. This can help me determine if there is a statistical or significant difference between groups, because I feel like I spend more time on a task in one sitting when I am with other people, so I think my mean productivity will be higher in the accompanied group.

## b. Visualization 


```{r}
#summarizing personal data
mydata_summary <-  mydata |> 
  group_by(accompanied) |> 
  summarise(mean_score = round(mean(final_productivity_score),digits = 1),
            sd = round(sd(final_productivity_score), digits = 1),
            se = round((sd(final_productivity_score)/sqrt(length(final_productivity_score))),digits = 1),
            ci_lower = round(mean_score - 1.96 * (sd(final_productivity_score)/ sqrt(length(final_productivity_score))),digits = 1),
            ci_upper = round(mean_score + 1.96 * (sd(final_productivity_score) / sqrt(length(final_productivity_score))),digits = 1)
  )



```


```{r}

#creating visualizations for personal data 

mydata_means <- ggplot(data = mydata,
                       aes(x = accompanied,
                           y = final_productivity_score,
                           color = accompanied)) +
  geom_jitter(height = 0,
              width = 0.2,
              shape = 1) +
  geom_errorbar(data = mydata_summary,
                aes(x = accompanied,
                    y = mean_score,
                    ymin = ci_lower,
                    ymax = ci_upper,
                    width = 0.15)) +
  geom_point(data = mydata_summary,
             aes(x = accompanied,
                 y = mean_score),
             inherit.aes = FALSE, 
             color = "black",
             size = 2) +
  labs(x = "Company Type",
       y = "Final Productivity Score",
       title = "Mean Productivity Score between \nAccompanied and Alone study sessions") +
  scale_color_manual(values = c("Accompanied" = "#377b42",
                                "Alone" = "#0c78bd")) +
  theme(legend.position = "none")

mydata_means



```








