---
title: "Homework 3"
author: "Jessi Rumkin"
date: "May 22, 2025"
format:
  html:
    toc: true # use this to display a table of contents
execute:
  message: false # use this to make sure messages don't show up
  warning: false # use this to make sure warnings don't show up
---

Link to GitHub repository:

# Set Up

```{r}
#read in packages
library(tidyverse)
library(here)
library(gt)
library(janitor)
library(readxl)

#read in data for personal data project
mydata <- read.csv("data/mydata.csv")

```

# Problem 1: Personal Data

## a. Data summarizing

I will be comparing the mean productivity score between two main groups, when I was alone and when I was accompanied for the study sessions in order to determine if working with other people increases my productivity, which is calculated from time spent working and how focused I was. This can help me determine if there is a statistical or significant difference between groups, because I feel like I spend more time on a task in one sitting when I am with other people, so I think my mean productivity will be higher in the accompanied group.

## b. Visualization

```{r}
#summarizing personal data
mydata_summary <-  mydata |> #make an object called mydata_summary using mydata file
  group_by(accompanied) |> #group the sumary by company type
  summarise(mean_score = round(mean(final_productivity_score),digits = 1), #find mean
            sd = round(sd(final_productivity_score), digits = 1), #find standard deviation
            se = round((sd(final_productivity_score)/sqrt(length(final_productivity_score))),digits = 1), #find standard error
            ci_lower = round(mean_score - 1.96 * (sd(final_productivity_score)/ sqrt(length(final_productivity_score))),digits = 1), #find lower confidence interval at 95%
            ci_upper = round(mean_score + 1.96 * (sd(final_productivity_score) / sqrt(length(final_productivity_score))),digits = 1) #find upper confidence interval at 95%
  )


```

```{r}

#creating visualizations for personal data, Figure 1.

mydata_means <- ggplot(data = mydata, #use ggplot to create a visualization called mydata_means with data from mydata
                       aes(x = accompanied,
                           y = final_productivity_score,
                           color = accompanied)) +
  geom_jitter(height = 0, #add geometry of jitter plot, 0 height jitter
              width = 0.2, #0.2 jitter width
              shape = 1) + #shape is open circles for the jitter points
  geom_errorbar(data = mydata_summary, #add a geometry of an error bar from data of mydata_summary
                aes(x = accompanied,
                    y = mean_score,
                    ymin = ci_lower,
                    ymax = ci_upper,
                    width = 0.15)) +
  geom_point(data = mydata_summary, #add geometry of a point from mydata_summary of the mean productivity score
             aes(x = accompanied,
                 y = mean_score),
             inherit.aes = FALSE, #the geom_point layer will not inherit aesthitcs settings
             color = "black", #point showing the mean is black
             size = 2) +
  labs(x = "Company Type", #labling the x and y axis and the title
       y = "Final Productivity Score",
       title = "Mean Productivity Score between \nAccompanied and Alone study sessions") +
  scale_color_manual(values = c("Accompanied" = "#377b42", #manual colors for groups 
                                "Alone" = "#0c78bd")) +
  theme(legend.position = "none") #removing the legend for redundancy

mydata_means #display the visualization


```

```{r}


# visualizing deadline type vs final productivity score
mydata_deadlinesummary <- mydata |> 
  group_by(deadline_type) |> 
  summarise(mean_score = mean(final_productivity_score))

mydata_deadline <- ggplot(data = mydata,
                          aes(x = deadline_type,
                              y = final_productivity_score,
                              color = deadline_type)) +
  geom_jitter(height = 0,
              width = 0.2,
              shape = 1) +
  geom_point(data = mydata_deadlinesummary,
             aes(x = deadline_type,
                 y = mean_score),
             inherit.aes = FALSE,
             color = "black",
             size = 2)


mydata_deadline

```

## c. Caption

**Figure 1. Average productivity scores are higher for accompanied study sessions compared to alone study sessions. ** The black point is the mean productivity score in each group, with error bars showing the confidence interval of the mean at a 95% confidence level, while open points represent individual data points. Colored by group type of accompanied (n = __) and alone (n = __)

## d. Table presentation

```{r}

#using gt package to make a table


```



